---
title: "DSA211_Project"
output: html_document
date: "2023-02-16"
format: html
editor_options: 
  markdown: 
    wrap: 90
---

# Scenario

Based on 2022 Singapore HDB resale price (real-life) data sets, your team is supposed to
construct a multiple regression model (for one particular district) to explain the HDB
resale price (ResalePrice) in dollars with the given independent variables.

-   Date: Transaction Month
-   Type: HDB Types (3-, 4- or 5-room flats)
-   Block: Block Number of Flat
-   Street: Flat's Street Location
-   Story: Flat's Story
-   Area: Size in Squared Meters
-   Model: Flat's Model
-   LeaseBegin: Year of Lease Start
-   LeaseRemain: Period of Lease Remaining

## Marking Criteria

Documentation and Presentation: 10 marks

Methodology: 10 marks

R-codes, computer outputs interpretation and graphical explanations: 15 marks

Recommendations and conclusions: 15 marks

## Format:

Written Report: PDF Format: Within 10pages excluding the cover page and Appendix

Appendix: codes with computer outputs

You are required to provide the detailed documentation of how you search your recommended
model for inference purpose and justify each step in your data analysis. You are also
expected to provide model assumption justification and hypothesis testing evidences
(R-codes and computer outputs) with clear explanations that your recommended model is the
best model among all the models considered according to BIC criterion. Based on your final
recommended model, state clearly your recommendations and conclusions.

# Part 1 of Project

Load Data In

```{r, echo = FALSE}
options(width = 100, wrap = "none")

pacman::p_load(dplyr, tmap, sf, jsonlite, readr)
```

```{r}
Sengkang1 <- read.csv("data/Sengkang2023P.csv", stringsAsFactors = TRUE)

head(Sengkang1, 5)
```
```{r}
library(httr)
geocode <- function(block, streetname) {
  base_url <- "https://developers.onemap.sg/commonapi/search"
  address <- paste(block, streetname, sep = " ")
  query <- list("searchVal" = address, 
                "returnGeom" = "Y",
                "getAddrDetails" = "N",
                "pageNum" = "1")
  
  res <- GET(base_url, query = query)
  restext<-content(res, as="text")
  
  output <- jsonlite::fromJSON(restext)  %>% 
    as.data.frame() %>%
    dplyr::select("results.LATITUDE", "results.LONGITUDE")
  return(output)
}
```

```{r, eval = FALSE}
Sengkang$LATITUDE <- 0
Sengkang$LONGITUDE <- 0

for (i in 1:nrow(Sengkang)){
  temp_output <- geocode(Sengkang[i, 3], Sengkang[i, 4])
  
  Sengkang$LATITUDE[i] <- temp_output$results.LATITUDE
  Sengkang$LONGITUDE[i] <- temp_output$results.LONGITUDE
}
```
```{r, eval = FALSE}
write_rds(Sengkang, file ="Sengkang_coords")
```
```{r}
Sengkang <- read_rds("Sengkang_coords")
```

```{r}
Sengkang_sf <- st_as_sf(Sengkang, coords = c("LONGITUDE", "LATITUDE"), crs = 4326) |>
    st_transform(crs = 3414)

glimpse(Sengkang_sf)
```

```{r}
library(tmap)
sengkang_sp <- Sengkang_sf %>%
  dplyr::select(3:11) %>%
  as_Spatial()
tmap_mode("view")

tm_shape(sengkang_sp) +
  tm_dots()
```
From the regression above, we know that there are too many categorical variables to
consider. We have to condense them accordingly.

```{r}
length(unique(Sengkang$Block))
length(unique(Sengkang$Street))
length(unique(Sengkang$LeaseRemain))
```

We can see from the code chunk above that block will have 521, street has 29 and
LeaseRemain has 226 categorical variables

# Data Wrangling
We will use the lubridate package to adjust the year and calculate lease years used as a numeric rather than a categorical variable. Since years_used and LeaseRemain are perfected correlated, we will drop LeaseRemaind from the dataframe. 

[site](https://www.mynicehome.gov.sg/lifestyle/places/navigating-the-vales-of-sengkang/),
the HDB blocks are numbered by 100+, 200+, 300+ and 400+ in Rivervale, Compassvale,
Anchorvale and Fernvale respectively.

```{r}
df <- Sengkang1 %>%
  mutate(Date = lubridate::ym(Date),
         LeaseBegin = lubridate::ym( paste0(LeaseBegin,"-01")),
         years_used = as.numeric((Date - LeaseBegin)/365),
         subzone = ifelse(grepl("^1", Block), "Rivervale",
                          ifelse(grepl("^2", Block), "Compassvale",
                                 ifelse(grepl("^3", Block), "Anchorvale",
                                        ifelse(grepl("4", Block), "Fernvale", "others")))),
         .before = Street) %>%
  mutate(subzone= as.factor(subzone),
         Date = as.factor(Date)) %>%
  select(-LeaseRemain, -LeaseBegin)
```

Using leaseremain as a factor will generate too many binary variables. Convert them into
years_used would be easier. Date and LeaseBegin variables must be in date type before
substracting between the two. The output would be in (drtn) days and thus we have to set
it to numeric set to years.

## Find the relationship between independent variables and Resale Price
```{r}
plot(df$Date, df$ResalePrice)
plot(df$Type, df$ResalePrice)
plot(df$Block, df$ResalePrice)
plot(df$years_used, df$ResalePrice)
plot(df$subzone, df$ResalePrice)
plot(df$Street, df$ResalePrice)
plot(df$Story, df$ResalePrice)
plot(df$Area, log(df$ResalePrice))
plot(df$Model, df$ResalePrice)

```

# Run Regression
## All variables
We will first calculate the BIC of the regression of all variables.
```{r}
reg_all <- lm(ResalePrice ~ ., data = df)
BIC(reg_all)
```
## Residual check
```{r}
r <- residuals(reg_all)
plot(df$Date, r,
     xlab = "Date", ylab = "Residuals")
plot(df$Type, r,
     xlab = "Type", ylab = "Residuals")
plot(df$Block, r,
     xlab = "Block", ylab = "Residuals")
plot(df$years_used, r,
     xlab = "years_used", ylab = "Residuals")
plot(df$subzone, r,
     xlab = "subzone", ylab = "Residuals")
plot(df$Street, r,
     xlab = "Street", ylab = "Residuals")
plot(df$Story, r,
     xlab = "Story", ylab = "Residuals")
plot(df$Area, r,
     xlab = "Area", ylab = "Residuals")
plot(df$Model, r,
     xlab = "Model", ylab = "Residuals")
```
From the residual plots above, we notice all plots points are scattered around the residual =0. This suggesrt that the model assumptions are not violated.
We have three types of location columns now, Block, Street and subzone. There should be high correlation between the X variables for these 3 variables, we will test the BIC number by dropping each variable out and picking the model with the lowest BIC
## Removing Block 
```{r}
L1 <- lm(ResalePrice ~ .-Block, data = df)
summary(L1)
```
## Removing Street
```{r}
L2 <- lm(ResalePrice ~ .-Street, 
         data = df)
summary(L2)
```
## Removing subzone
```{r}
L3 <- lm(ResalePrice ~ .-subzone, 
         data = df)
summary(L3)
```
It would seem removing Block would be the best. Now we will compare between street and subzone
## Removing Block and Street
```{r}
L4 <- lm(ResalePrice ~ .-Block-Street, 
         data = df)
summary(L4)
```

## Removing Block and subzone
```{r}
L5 <- lm(ResalePrice ~ .-Block-subzone, data = df)
summary(L5)
```

### Comparing BIC
```{r}
BIC_location <- data.frame(lm = c(".-Block",".-Street",".-subzone",".-Block-Street",".-Block-subzone"),
                              BIC = c(BIC(L1),BIC(L2),BIC(L3),BIC(L4),BIC(L5)))
BIC_location
```
# Checking for multicolinearity
We will notice that L4 and L5 have no perfect collinearity in the model. However, under L1, there was only one perfect collinearity found. 
Using our best model so far, L1, we need to fix the perfect multicolinearity present.
We notice from above that L1 in fact, has perfect collinearity between Street and subzone. We will wrangle the data such that we can ommit one street while assign a binary variable to them. We will drop two of the street to ensure we do not have perfect collinerity. It is important to choose streets with a high p-value so as to see the effects of the more significant streets.

```{r}
df_1 <- df %>%
  tidyr::pivot_wider(names_from = Street,
              values_from = Street, 
              values_fn = list(Street = ~1), 
              values_fill = 0) 
```

```{r}
# Run L1 again with new df
L1_modified <- lm(ResalePrice ~.-Block,
                  data = df_1)
summary(L1_modified)
# It is understood that Street and Subzone will be correlated. We will remove two variables from Street and rerun
```
```{r}
# We will choose ANCHORVALE LANE and FERNVALE RD that have a corresponding p-value of
L6 <- lm(ResalePrice ~.-Block-`ANCHORVALE LANE`-`FERNVALE RD`,
         data = df_1)
summary(L6)
BIC(L6)
```
We notice that after removing the 2 variables BIC lowers to 49873.17, lower than initially calculated. We also see that adjusted R square maintains at 0.8857. 

```{r}
library(car)

v <- vif(L6)
v
```
Generally, GVIF above 2 or 3 to suggest potential multi-collinearity. Given that Street and subzone is correlated in some ways due to roads intersections with the subzones, we will bound to see some collinearity there. However, both categories are still useful for its own interpretation. For example, subzone indicates neighbourhoods clustering. There could be other variables such as proximity of schools, clinics and other facilities that attribute to the popularity of the subzone. As for streets, it could be that some streets have more buses operating or that some streets leads to expressway, contributing to ease of commute. hence, even though there are some VIF scores of 5, they are still within acceptable basis.

Next, we need to consider Type and Area
Area is positively related to Type.

## Visualize L6
```{r}
plot(L6)
```

Note: We will be using L1 as the main regression and adding on to that regression. We know that the model is linear as checked under residual plots assumptions. 

```{r}
library(fitdistrplus)
fnorm <- fitdist(residuals(L6), "norm")
result <- gofstat(fnorm, discrete = FALSE)
result
```
```{r}
KScritvalue <-1.36/sqrt(length(df$Date))
KScritvalue

summary(fnorm)
plot(fnorm)
```

Since KS statistics = 0.032744 > 0.02956522=Kcrit, we can reject the null hypothesis and thus the data do provide sufficient evidence to show the normal model is the appropriate model.



## To test correlation between street and subzone
```{r}
1 +1
```










