---
title: "DSA211_Project"
output: html_document
date: "2023-02-16"
---

# Scenario
Based on 2022 Singapore HDB resale price (real-life) data sets, your team is supposed to construct a multiple regression model (for one particular district) to explain the HDB resale price (ResalePrice) in dollars with the given independent variables.
  Date: Transaction Month
  Type: HDB Types (3-, 4- or 5-room flats) 
  Block: Block Number of Flat
  Street: Flat’s Street Location
  Story: Flat’s Story
  Area: Size in Squared Meters
  Model: Flat’s Model
  LeaseBegin: Year of Lease Start
  LeaseRemain: Period of Lease Remaining


In your written report (it must be in pdf-format and within 10 pages, excluding the cover page and codes with computer outputs in Appendix), you are required to provide the detailed documentation of how you search your recommended model for inference purpose and justify each step in your data analysis. You are also expected to provide model assumption justification and hypothesis testing evidences (R-codes and computer outputs) with clear explanations that your recommended model is the best model among all the models considered according to BIC criterion. Based on your final recommended model, state clearly your recommendations and conclusions.
## Marking Criteria
Documentation and Presentation: 10 marks
Methodology: 10 marks
R-codes, computer outputs interpretation and graphical explanations: 15 marks 
Recommendations and conclusions: 15 marks


# Load Data in
```{r}
Sengkang <- read.csv("data/Sengkang2023P.csv", stringsAsFactors = TRUE)
summary(Sengkang)
```

```{r}
2+2
```


